Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-12-18 apj.tex
reassembling note

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The two color parameters exhibit the behavior expected from the two-parameter
\citet{1999PASP..111...63F} dust model.
The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Extending the model to three color parameters gives almost identical results for
the two parameters
plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
beyond those tracked by the spectral features and two-parameter dust models.
\end{abstract}

@@

SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6098 \pm   4$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\

@@

PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6141 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\

@@

@@

PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6114 \pm   9$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\

@@

PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6168 \pm   6$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\

@@

@@

@@

SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6127 \pm  10$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6144 \pm   2$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\

@@

SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   4$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\

@@

SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6112 \pm   2$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\

@@

SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6148 \pm   4$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\

@@

SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6129 \pm   7$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\

@@

\section{Supernova Model I: Two Extrinsic Parameters}
\label{model:sec}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameter & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{+0.0009}_{-0.0009}$
&
$0.0016^{+0.0007}_{-0.0007}$
&
$0.0015^{+0.0006}_{-0.0006}$
&
$0.0015^{+0.0005}_{-0.0005}$
&
$0.0026^{+0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{+   1.0}_{  -0.5}$
&
$   0.1^{+   0.1}_{  -0.2}$
&
\ldots
&
$  -0.0^{+   0.1}_{  -0.1}$
&
$   0.7^{+   0.7}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{+ 0.003}_{-0.003}$
&
$ 0.025^{+ 0.002}_{-0.003}$
&
$ 0.025^{+ 0.002}_{-0.002}$
&
$ 0.020^{+ 0.002}_{-0.002}$
&
$ 0.019^{+ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.26^{+  0.05}_{ -0.05}$
&
$ -0.01^{+  0.03}_{ -0.03}$
&
\ldots
&
$ -0.19^{+  0.01}_{ -0.01}$
&
$ -0.24^{+  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{+0.0012}_{-0.0011}$
&
$-0.0000^{+0.0010}_{-0.0009}$
&
$0.0005^{+0.0008}_{-0.0008}$
&
$0.0005^{+0.0007}_{-0.0007}$
&
$-0.0003^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.40^{+  2.33}_{ -1.90}$
&
$ -0.34^{+  1.60}_{ -1.20}$
&
\ldots
&
$ -0.11^{+  0.29}_{ -0.27}$
&
$ -0.84^{+  1.66}_{ -1.27}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{+  0.06}_{ -0.05}$
&
$  0.35^{+  0.03}_{ -0.03}$
&
\ldots
&
$ -0.23^{+  0.01}_{ -0.01}$
&
$ -0.45^{+  0.03}_{ -0.03}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.31^{+  0.17}_{ -0.18}$
&
$ -0.17^{+  0.09}_{ -0.10}$
&
\ldots
&
$ -0.07^{+  0.05}_{ -0.04}$
&
$ -0.17^{+  0.10}_{ -0.09}$
\\
$\sigma_X$
&
$ 0.060^{+ 0.012}_{-0.012}$
&
$ 0.033^{+ 0.007}_{-0.007}$
&
$ 0.021^{+ 0.004}_{-0.006}$
&
$ 0.012^{+ 0.007}_{-0.008}$
&
$ 0.044^{+ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model in \S\ref{model:sec}.\label{global:tab}}
\end{table}

@@

Non-trivial residual magnitude dispersions are captured in $C_c$.  The diagonal elements are captured by the $\sigma$ parameters;
the residual intrinsic dispersion ranges from
$\sim 0.01$ to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.  Given that the 
off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix rather than the matrix elements themselves,
it is not straightforward to present correlation matrix confidences:
the average over Monte Carlo links of the
Cholesky factors will not  generally yield a correlation matrix.  
To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
chain, element by element.
For $UBVRI$ the matrix is
\begin{equation}
C_c(U,B,V,R,I)=
\begin{pmatrix}
\begin{array}{rrrrr}
0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
0.0010 & 0.0011 & 0.0002 & -0.0000 & -0.0006 \\
-0.0002 & 0.0002 & 0.0004 & 0.0000 & -0.0002 \\
-0.0000 & -0.0000 & 0.0000 & 0.0002 & 0.0002 \\
0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
\end{array}
 \end{pmatrix} \text{mag}^2.
 \label{mag_cov:eqn}
 \end{equation}
\color{red}
The average correlation matrix is
\begin{equation}
Cor(U,B,V,R,I)=
\begin{pmatrix}
\begin{array}{rrrrr}
1.00 & 0.43 & -0.17 & -0.06 & 0.10 \\
0.43 & 1.00 & 0.24 & -0.09 & -0.41 \\
-0.17 & 0.24 & 1.00 & 0.09 & -0.22 \\
-0.06 & -0.09 & 0.09 & 1.00 & 0.25 \\
0.10 & -0.41 & -0.22 & 0.25 & 1.00
\end{array}
 \end{pmatrix}.
 \end{equation}
 \color{black}
The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
expressed as the standard deviations and
 correlation matrix
 \begin{equation}
 \sigma(U-V, B-V, V-R, V-I)=
 \begin{pmatrix}
0.068 & 0.034& 0.023 & 0.053
  \end{pmatrix} \text{mag}
 \label{color_sd:eqn}
   \end{equation}
 \begin{equation}
 Cor(U-V, B-V, V-R, V-I)=
\begin{pmatrix}
\begin{array}{rrrr}
1.000 & 0.615 & -0.334 & -0.296 \\
0.615 & 1.000 & -0.193 & 0.099 \\
-0.334 & -0.193 & 1.000 & 0.634 \\
-0.296 & 0.099 & 0.634 & 1.000 
\end{array}
\end{pmatrix}.
  \label{color_cor:eqn}
 \end{equation}
These color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}, for cases where direct comparison can be made.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
\begin{pmatrix}
\begin{array}{rrrrrr}
1.00 & 0.00 & -0.06 & -0.05 & 0.11 & 0.01 \\
0.00 & 1.00 & 0.11 & -0.25 & -0.07 & -0.00 \\
-0.06 & 0.11 & 1.00 & -0.14 & -0.16 & -0.03 \\
-0.05 & -0.25 & -0.14 & 1.00 & 0.04 & 0.03 \\
0.11 & -0.07 & -0.16 & 0.04 & 1.00 & 0.06 \\
0.01 & -0.00 & -0.03 & 0.03 & 0.06 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}
We find weak correlations between our color-excess parameters and the input features, the strongest being $-0.16$ between
$E_\gamma(B-V)$ and $EW_{Si}$.
Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
and \citet{leget:thesis}.

@@

\color{red}
Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
means of $k_0$ and $k_1$ to zero.
There are unconstrained $k_0^0$, $k_1^0$ that correspond to an intrinsic supernova.  The true extinction is
$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
relating $A_V$ and $E(B-V)$.
\color{black}
Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.
\color{red}
The slope uncertainties are the $68$\% credible interval from the Bayesian analysis and does not incorporated goodness
 of fit.  Indeed,
the full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.

\color{blue}
Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
$A_V=0$, and such that the ridge line 
has close to constant $R^T_V$.
\color{black}
With this ansatz, we
estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
 \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
\color{black}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/avebv.pdf}
   \includegraphics[width=2.8in]{output11/rv.pdf}
   \caption{
	\color{red}
   Left: $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data. Right: Shown for qualitative purposes,
   $R^T_V=A^T_V/E^T(B-V)$ 
   versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
   %Overplotted is the mean and standard deviation of those points in equally divided bins.
   On both plots are overplotted the expected values for the \citetalias{1999PASP..111...63F} model
   for specific choices of $R^F_V$, normalized to have $A_V=0$ at $E(B-V)=0$.  Note that these lines are not straight on the left plot, and are not constant on the plot to the right.
   \color{black}
   \label{avebv:fig}}
\end{figure}

Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
parameters of a single  dust model.
\color{red}
Our model for broadband photometry does not specify how spectral features and color parameters affect the supernova spectrum, information
necessary to predict the magnitude extinction of dust models.
\color{blue}
The lack of correspondence between dust models and broadband extinction is quantified when we apply an $R^F_V=2.5$ SN-frame dust to the
observed spectra used in our sample, to yield a distribution in the quantity $R_V=A_V/(A_B-A_V)$ with mean and standard deviation of $3.11 \pm 0.35$.
While an accurate study of fundamental dust properties would incorporate the dust law within the model itself, we now proceed nonetheless
in making a connection between our model outputs and dust.

\color{red}
Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R^T_V$ for $R^F_V=1.1, 1.9, 2.5, 3.1$
within the context of the \citetalias{1999PASP..111...63F} model.
Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
non-linear, and $R^T_V$ is not constant for a fixed value of $R^F_V$.
\color{black}

>>>>

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The two color parameters exhibit the behavior expected from the two-parameter
\citet{1999PASP..111...63F} dust model.
The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Extending the model to three color parameters gives almost identical results for
the two parameters
plus a detection of a third parameter at
%--- table.py
$>95$\% confidence;
%-----
this new parameter is responsible for supernova color diversity
beyond those tracked by the spectral features and two-parameter dust models.
\end{abstract}

@@

SN2007bd & $109.7 \pm 5.9$ & $ 17.5 \pm 0.7$& $ 6101 \pm   3$ & $-29.31 \pm   0.01$ & $-29.12 \pm   0.01$& $-28.60 \pm   0.01$& $-28.35 \pm   0.01$& $-27.60 \pm   0.01$ \\

@@

PTF10ops & $ 38.7 \pm 9.9$ & $  7.2 \pm 8.7$& $ 6140 \pm   5$ & $-27.93 \pm   0.38$ & $-27.76 \pm   0.38$& $-27.73 \pm   0.38$& $-27.59 \pm   0.38$& $-27.21 \pm   0.38$ \\

@@

PTF12efn & $144.9 \pm 3.4$ & $  7.1 \pm 1.8$& $ 6115 \pm   3$ & $-29.40 \pm   0.01$ & $-29.17 \pm   0.01$& $-28.79 \pm   0.01$& $-28.45 \pm   0.01$& $-27.64 \pm   0.01$ \\

@@

PTF13ayw & $104.6 \pm 2.4$ & $ 26.6 \pm 3.2$& $ 6115 \pm   6$ & $-29.16 \pm   0.02$ & $-28.82 \pm   0.02$& $-28.43 \pm   0.02$& $-28.20 \pm   0.02$& $-27.55 \pm   0.02$ \\

@@

PTF11mkx & $ 31.5 \pm 3.7$ & $  4.5 \pm 1.3$& $ 6169 \pm   5$ & $-29.50 \pm   0.45$ & $-29.25 \pm   0.45$& $-28.89 \pm   0.45$& $-28.61 \pm   0.45$& $-27.97 \pm   0.45$ \\

@@

SNF20061024-000 & $ 86.9 \pm 26.8$ & $ 30.0 \pm 1.5$& $ 6127 \pm   5$ & $-28.88 \pm   0.04$ & $-28.70 \pm   0.04$& $-28.26 \pm   0.04$& $-28.05 \pm   0.04$& $-27.40 \pm   0.04$ \\

@@

SNF20061011-005 & $120.6 \pm 1.1$ & $  9.3 \pm 0.4$& $ 6132 \pm   4$ & $-29.72 \pm   0.04$ & $-29.43 \pm   0.03$& $-28.99 \pm   0.03$& $-28.64 \pm   0.03$& $-27.90 \pm   0.03$ \\

@@

SNF20080516-000 & $117.4 \pm 2.2$ & $  9.0 \pm 1.2$& $ 6135 \pm   3$ & $-29.50 \pm   0.01$ & $-29.23 \pm   0.01$& $-28.80 \pm   0.01$& $-28.47 \pm   0.01$& $-27.74 \pm   0.01$ \\
SN2005cf & $159.1 \pm 0.7$ & $ 15.7 \pm 0.8$& $ 6141 \pm   3$ & $-29.37 \pm   0.02$ & $-29.16 \pm   0.02$& $-28.68 \pm   0.02$& $-28.41 \pm   0.02$& $-27.69 \pm   0.02$ \\

@@

SNF20080620-000 & $107.8 \pm 14.1$ & $ 20.0 \pm 0.7$& $ 6132 \pm   3$ & $-28.82 \pm   0.02$ & $-28.78 \pm   0.01$& $-28.32 \pm   0.01$& $-28.09 \pm   0.01$& $-27.39 \pm   0.01$ \\

@@

SNF20080720-001 & $138.5 \pm 4.0$ & $ 14.0 \pm 2.0$& $ 6107 \pm   3$ & $-27.59 \pm   0.02$ & $-27.78 \pm   0.01$& $-27.73 \pm   0.01$& $-27.71 \pm   0.01$& $-27.19 \pm   0.02$ \\

@@

SNF20061022-005 & $ 64.6 \pm 3.8$ & $  3.7 \pm 1.4$& $ 6146 \pm   7$ & $-29.49 \pm   0.02$ & $-29.06 \pm   0.02$& $-28.71 \pm   0.02$& $-28.42 \pm   0.02$& $-27.93 \pm   0.02$ \\

@@

SNF20050624-000 & $121.0 \pm 5.3$ & $  9.3 \pm 3.1$& $ 6126 \pm   6$ & $-29.75 \pm   0.01$ & $-29.42 \pm   0.01$& $-28.99 \pm   0.01$& $-28.68 \pm   0.01$& $-27.97 \pm   0.01$ \\
SNF20060618-023 & $ 74.9 \pm 4.9$ & $  5.0 \pm 1.8$& $ 6137 \pm  21$ & $-29.61 \pm   0.02$ & $-29.18 \pm   0.02$& $-28.89 \pm   0.02$& $-28.66 \pm   0.02$& $-28.08 \pm   0.02$ \\

@@

\section{Supernova Model I: Two Extrinsic Parameters}
\label{model:sec}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameter & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{+0.0009}_{-0.0009}$
&
$0.0016^{+0.0008}_{-0.0007}$
&
$0.0015^{+0.0006}_{-0.0006}$
&
$0.0015^{+0.0005}_{-0.0005}$
&
$0.0027^{+0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{+   1.1}_{  -0.5}$
&
$   0.1^{+   0.1}_{  -0.2}$
&
$\dots$
&
$   0.0^{+   0.1}_{  -0.1}$
&
$   0.8^{+   0.8}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{+ 0.003}_{-0.003}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.026^{+ 0.002}_{-0.002}$
&
$ 0.021^{+ 0.002}_{-0.002}$
&
$ 0.020^{+ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.25^{+  0.05}_{ -0.05}$
&
$ -0.01^{+  0.03}_{ -0.03}$
&
$\dots$
&
$ -0.19^{+  0.01}_{ -0.01}$
&
$ -0.23^{+  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{+0.0012}_{-0.0011}$
&
$0.0000^{+0.0010}_{-0.0009}$
&
$0.0005^{+0.0008}_{-0.0008}$
&
$0.0006^{+0.0007}_{-0.0007}$
&
$-0.0002^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.39^{+  2.22}_{ -1.82}$
&
$ -0.35^{+  1.58}_{ -1.20}$
&
$\dots$
&
$ -0.09^{+  0.29}_{ -0.28}$
&
$ -0.78^{+  1.48}_{ -1.11}$
\\
$\gamma^0_X$
&
$ 63.46^{+  3.70}_{ -3.66}$
&
$ 51.40^{+  3.09}_{ -3.07}$
&
$ 38.15^{+  2.70}_{ -2.63}$
&
$ 29.26^{+  2.40}_{ -2.35}$
&
$ 20.94^{+  2.24}_{ -2.25}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{+  0.06}_{ -0.05}$
&
$  0.35^{+  0.03}_{ -0.03}$
&
$\dots$
&
$ -0.23^{+  0.01}_{ -0.02}$
&
$ -0.45^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$-10.34^{+  3.61}_{ -4.29}$
&
$-11.89^{+  2.95}_{ -3.56}$
&
$-14.48^{+  2.47}_{ -2.89}$
&
$-13.71^{+  2.14}_{ -2.45}$
&
$-12.51^{+  2.10}_{ -2.23}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.28^{+  0.17}_{ -0.19}$
&
$ -0.18^{+  0.10}_{ -0.10}$
&
$\dots$
&
$ -0.05^{+  0.05}_{ -0.04}$
&
$ -0.14^{+  0.10}_{ -0.09}$
\\
$\sigma_X$
&
$ 0.060^{+ 0.012}_{-0.012}$
&
$ 0.033^{+ 0.007}_{-0.007}$
&
$ 0.021^{+ 0.004}_{-0.005}$
&
$ 0.011^{+ 0.008}_{-0.007}$
&
$ 0.044^{+ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model in \S\ref{model:sec}.\label{global:tab}}
\end{table}

@@

Non-trivial residual magnitude dispersions are captured in $C_c$.  The diagonal elements are captured by the $\sigma$ parameters;
the residual intrinsic dispersion ranges from
$\sim 0.01$ to 0.06 mag, significantly smaller
than the dispersion in $\Delta$.  Given that the 
off-diagonal elements of $C_c$ are parameterized by the Cholesky factors of a correlation matrix rather than the matrix elements themselves,
it is not straightforward to present correlation matrix confidences:
the average over Monte Carlo links of the
Cholesky factors will not  generally yield a correlation matrix.  
To characterize a typical posterior draw of $C_c$ we use the matrix that is the mean of all covariance realizations in the
chain, element by element.
For $UBVRI$ the matrix is
\begin{equation}
C_c(U,B,V,R,I)=
\begin{pmatrix}
\begin{array}{rrrrr}
0.0038 & 0.0010 & -0.0002 & -0.0000 & 0.0003 \\
0.0010 & 0.0011 & 0.0002 & -0.0000 & -0.0006 \\
-0.0002 & 0.0002 & 0.0004 & 0.0000 & -0.0002 \\
-0.0000 & -0.0000 & 0.0000 & 0.0002 & 0.0002 \\
0.0003 & -0.0006 & -0.0002 & 0.0002 & 0.0020
\end{array}
 \end{pmatrix} \text{mag}^2.
 \label{mag_cov:eqn}
 \end{equation}
\color{red}
The average correlation matrix is
\begin{equation}
Cor(U,B,V,R,I)=
\begin{pmatrix}
\begin{array}{rrrrr}
1.00 & 0.42 & -0.18 & -0.05 & 0.12 \\
0.42 & 1.00 & 0.26 & -0.09 & -0.39 \\
-0.18 & 0.26 & 1.00 & 0.09 & -0.22 \\
-0.05 & -0.09 & 0.09 & 1.00 & 0.27 \\
0.12 & -0.39 & -0.22 & 0.27 & 1.00
\end{array}
 \end{pmatrix}.
 \end{equation}
 \color{black}
The  covariance of the colors $U-V$, $B-V$, $V-R$, and $V-I$ is
expressed as the standard deviations and
 correlation matrix
 \begin{equation}
 \sigma(U-V, B-V, V-R, V-I)=
 \begin{pmatrix}
0.068 & 0.034 & 0.023 & 0.053
  \end{pmatrix} \text{mag}
 \label{color_sd:eqn}
   \end{equation}
 \begin{equation}
 Cor(U-V, B-V, V-R, V-I)=
\begin{pmatrix}
\begin{array}{rrrr}
1.000 & 0.602 & -0.353 & -0.317 \\
0.602 & 1.000 & -0.197 & 0.082 \\
-0.353 & -0.197 & 1.000 & 0.647 \\
-0.317 & 0.082 & 0.647 & 1.000
\end{array}
\end{pmatrix}.
  \label{color_cor:eqn}
 \end{equation}
These color variances are smaller than those derived by \citet{2003A&A...404..901N, 2007ApJ...659..122J}, for cases where direct comparison can be made.

@@

The Pearson correlation coefficients for $\Delta$, $EW_{Ca}$, $EW_{Si}$, $\lambda_{Si}$, $E_{\gamma^0}(B-V)$, and $E_{\gamma^0}(B-V)$ are given in the matrix
\begin{multline}
Cor(\Delta, EW_{Ca}, EW_{Si}, \lambda_{Si}, E_{\gamma^0}(B-V), E_{\gamma^1}(B-V)) =\\
\begin{pmatrix}
\begin{array}{rrrrrr}
1.00 & 0.00 & -0.06 & -0.05 & 0.11 & 0.01 \\
0.00 & 1.00 & 0.10 & -0.26 & -0.07 & -0.01 \\
-0.06 & 0.10 & 1.00 & -0.14 & -0.17 & -0.03 \\
-0.05 & -0.26 & -0.14 & 1.00 & 0.03 & 0.03 \\
0.11 & -0.07 & -0.17 & 0.03 & 1.00 & 0.05 \\
0.01 & -0.01 & -0.03 & 0.03 & 0.05 & 1.00
\end{array}
\end{pmatrix}.
\end{multline}
We find weak correlations between our color-excess parameters and the input features, the strongest being
%---
$-0.17$
%---
 between
$E_\gamma(B-V)$ and $EW_{Si}$.
Recall that $EW_{Si}$ is correlated with light-curve shape, which is correlated with host-galaxy (including dust) properties 
\citep{2000AJ....120.1479H, 2003MNRAS.340.1057S}.
An extensive discussion of the correlations between the spectral features of the SNfactory data set can be found in \citet{chotard:thesis}
and \citet{leget:thesis}.

@@

\color{blue}
Recall that there are degeneracies between the intrinsic (Eqn.~\ref{ewsiv:eqn}) and
extrinsic (Eqn.~\ref{dust:eqn}) parameters of our model.  Part of that degeneracy is
broken by imposing $\langle k_0 \rangle=0$ and  $\langle k_1 \rangle=0$,
but this choice does not specify the $k_0^0$, $k_1^0$ corresponding to supernovae experiencing no extrinsic effects.  The true extrinsic
extinction is
$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
The true extrinsic color excess is $E^T(B-V) = A^T_B-A^T_V$, so that the total-to-selective extinction is $R^T_V=A^T_V/E^T(B-V)$.
Our model as analyzed cannot directly determine the above extrinsic properties per supernova.

Nevertheless, we are able to examine aggregate properties of the extinction.  The extrinsic extinction and color relation can be
written as
$$A_X(k_0,k_1) = R^T_V \left( A_B(k_0,k_1) -  A_V(k_0,k_1)\right) -R^T_V \left(A_B(k^0_0,k^0_1) + A_V(k^0_0,k^0_1)\right)+  A_X(k^0_0,k^0_1) .
$$
Making the assumption that $R^T_V$ is the same for all supernovae (shown later to be approximately true for dust laws),
it can be determined as the slope of the relation between $A_X$ and $E(B-V)$.
\color{black}
Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of
%----- fitz11.py
$R_V=2.77 \pm 0.08$.
%----
\color{blue}
The slope uncertainties are the $68$\% credible interval from the Bayesian analysis and does not incorporated goodness
 of fit.  Indeed,
the full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.

%\begin{comment}
%\color{blue}
%Our model alone cannot determine $R^T_V = A^T_V/E^T(B-V)$ for individual objects, as $k_0^0$ and $k_1^0$ are unconstrained.
%For a qualitative view, we choose zeros  such that the $V$-band extinction and color-excess of the bluest supernova roughly correspond to $E(B-V)=0$,
%$A_V=0$, and such that the ridge line 
%has close to constant $R^T_V$.
%\color{black}
%With this ansatz, we
%estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
% \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F})  model for fixed $R^F_V$ overplotted.
%With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
%We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
%of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
%A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
%for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
%\color{black}
%
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output11/avebv.pdf}
   %\includegraphics[width=2.8in]{output11/rv.pdf}
   \caption{
	\color{red}
   $A_V$ versus $E(B-V)$, and the slope $R_V$ of the linear fit to the data.
   %Right: Shown for qualitative purposes,
   %$R^T_V=A^T_V/E^T(B-V)$ 
   %versus $E^T(B-V)$ for the supernova sample, given an ansatz for the definition of an intrinsic supernova. 
   %Overplotted is the mean and standard deviation of those points in equally divided bins.
   Overplotted the expected values for the \citetalias{1999PASP..111...63F} model
   for specific choices of $R^F$.  Note that these lines are not straight on the left plot.
   \color{black}
   \label{avebv:fig}}
\end{figure}
%\end{comment}

We now compare our model and its color-parameters $k_0$ and $k_1$ with the expectations of  dust laws,
in contrast to  empirical properties derived from our model.
A direct analysis of the  \citetalias{1999PASP..111...63F} dust model is presented later
in \S\ref{model0:sec}.

%Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
%parameters of a single  dust model.
%\color{red}
%Our model for broadband photometry does not specify how spectral features and color parameters affect the supernova spectrum, information
%necessary to predict the magnitude extinction of dust models.
%\color{blue}
%The lack of correspondence between dust models and broadband extinction is quantified when we apply an $R^F_V=2.5$ SN-frame dust to the
%observed spectra used in our sample, to yield a distribution in the quantity $R_V=A_V/(A_B-A_V)$ with mean and standard deviation of $3.11 \pm 0.35$.
%While an accurate study of fundamental dust properties would incorporate the dust law within the model itself, we now proceed nonetheless
%in making a connection between our model outputs and dust.
